\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{calc}
\begin{document}
\textbf{Temperature Scaling Is Not Enough:}

\textbf{Calibration Gaps Under Human Label Distributions}

Wisdom Dogah*$^\dagger$

June 2026

\emph{*University of Mines and Technology (UMaT), Tarkwa, Ghana.}

\emph{$^\dagger$Correspondence: wisdom@blackmatrix.io.}

\textbf{Abstract}

\begin{quote}
Temperature scaling is the dominant post-hoc calibration method in
modern deep learning. Its theoretical justification rests on an
assumption that is rarely stated explicitly: that ground-truth labels
are one-hot and deterministic. In practice, labels are frequently soft,
crowd-sourced, or genuinely distributional, reflecting real disagreement
among human annotators rather than annotation noise. We study whether
temperature scaling retains its calibration properties when this
assumption is violated, and whether any resulting degradation depends on
model scale. Using CIFAR-10H and ChaosNLI, two publicly available
datasets with human-annotated soft label distributions, we evaluate
three model scales per modality under both hard one-hot and soft
distributional label targets. Across all nine configurations we observe
a positive soft-label calibration gap: temperature scaling calibrated on
hard labels consistently underperforms an oracle calibrated directly on
soft labels, with a Brier Score gap ranging from 0.002 to 0.134. The gap
increases monotonically with model scale in the vision domain and on the
SNLI-derived ChaosNLI split, and is substantially larger in the language
domain (mean gap 0.079) than in the vision domain (mean gap 0.003). A
scale-ordering anomaly on the MNLI-derived split reverses the expected
trend; we attribute this to a task-difficulty confound arising from
cross-domain evaluation. These findings suggest that calibration
validation protocols built on majority-vote labels can systematically
misstate model reliability in domains where label ambiguity is
structural rather than incidental.

\emph{\textbf{Keywords:} calibration; temperature scaling; soft labels;
label ambiguity; Expected Calibration Error; Brier Score; model scale;
uncertainty quantification.}
\end{quote}

\textbf{1. Introduction}

A probabilistic classifier is well-calibrated when its predicted
confidence matches empirical accuracy: among all predictions assigned
confidence \emph{p}, approximately a fraction \emph{p} should be correct
{[}5{]}. In safety-critical applications, a miscalibrated model that is
confidently wrong is more dangerous than an uncertain model that
correctly signals its own ignorance. The consequences of overconfident
incorrect predictions are well documented in medical imaging, content
moderation, and judicial risk assessment.

Temperature scaling {[}7{]} is the most widely deployed post-hoc
calibration method for neural networks. A single scalar parameter
\emph{T} is fit by minimizing negative log-likelihood on a validation
set, and logits are divided by \emph{T} before the softmax at inference
time. The method adds no parameters and requires no retraining, which
accounts for its near-universal adoption. Its limitation, which we
measure in this paper, is that its optimization target implicitly
assumes ground-truth labels are one-hot and deterministic.

This assumption fails whenever a labeling task involves genuine human
disagreement, such that the correct answer is not a single class but a
distribution over plausible answers {[}1{]}. Two datasets make this
disagreement explicit. CIFAR-10H {[}13{]} provides per-image soft label
distributions for the CIFAR-10 test set, derived from a mean of 51 human
annotations per image. ChaosNLI {[}10{]} provides 100 human judgments
per instance for natural language inference examples that exhibit
substantial semantic ambiguity. A model that assigns high confidence to
a single class when human annotators are evenly split is not calibrated
in any meaningful sense, even when its predicted class coincides with
the majority vote.

We conduct a controlled measurement study to test whether temperature
scaling, calibrated against hard one-hot labels, remains an effective
calibration strategy when evaluated against soft, distributional
targets, and whether any degradation scales with model capacity.

\textbf{1.1 Hypotheses}

We test three pre-specified hypotheses, introduced here and evaluated in
Section 5.

\begin{quote}
H1 (Gap existence). Temperature scaling calibrated on hard labels yields
a strictly worse Brier Score against the soft label distribution than an
oracle calibrated directly on soft labels. We refer to this difference
as the soft-label calibration gap and define it formally in Section 3.4.

H2 (Scale dependence). The soft-label calibration gap increases
monotonically with model scale within each dataset, consistent with the
established finding that larger models tend toward higher confidence
{[}7{]}.

H3 (Modality dependence). The soft-label calibration gap is larger in
the language domain (ChaosNLI) than in the vision domain (CIFAR-10H),
reflecting the comparatively higher rate of genuine semantic ambiguity
in natural language inference relative to object classification.
\end{quote}

\textbf{1.2 Contributions}

\begin{quote}
We formalize the soft-label calibration gap as a measurable quantity and
provide a protocol for estimating it using existing soft-label datasets
(Section 3).

We report a systematic cross-scale measurement of this gap across two
modalities and two soft-label resources (Section 5).

We identify and analyze a scale-ordering anomaly on the MNLI-derived
ChaosNLI split, attributing it to a cross-domain evaluation confound
rather than a genuine reversal of H2 (Section 5.3).

We discuss practical implications for calibration methodology and
deployment in resource-constrained, ambiguous-label settings (Section
6).
\end{quote}

\textbf{2. Related Work}

\textbf{2.1 Calibration of Neural Networks}

Guo et al. {[}7{]} established that modern deep networks are
substantially more overconfident than earlier architectures and proposed
temperature scaling as an effective post-hoc correction. Subsequent work
has proposed isotonic regression, Platt scaling {[}11{]}, and Dirichlet
calibration {[}8{]} as alternatives. Minderer et al. {[}9{]} found that
Vision Transformers tend to be better calibrated in-distribution than
convolutional architectures. Bai et al. {[}2{]} showed analytically that
overconfidence is not solely a consequence of overparameterization.
Kumar et al. {[}6{]} showed that ECE tends to underestimate true
miscalibration due to binning artifacts, motivating our use of Brier
Score as a complementary metric.

\textbf{2.2 Soft Labels and Human Disagreement}

Work on learning from crowds {[}15{]} and annotation disagreement
{[}1{]} has established that human label variation carries information
about task ambiguity. Peterson et al. {[}13{]} introduced CIFAR-10H. Nie
et al. {[}10{]} introduced ChaosNLI to surface genuine semantic
ambiguity that majority-vote labeling obscures. Their systematic use as
calibration benchmarks under distributional targets is, to the best of
our knowledge, the specific contribution of this paper.

\textbf{2.3 Calibration Under Distribution Shift}

Ovadia et al. {[}12{]} showed that calibration degrades under dataset
shift even where accuracy is partially preserved. Guillory et al.
{[}4{]} found that confidence-based accuracy estimators degrade under
natural distribution shift. Wiles et al. {[}3{]} showed that larger
models and larger pretraining corpora tend to improve both OOD accuracy
and calibration under standard protocols. None of this work examines the
case in which the shift occurs in the label distribution rather than the
input distribution.

\textbf{3. Problem Formulation}

\textbf{3.1 Notation}

Let X be the input space and Y = \{1, \ldots, K\} the label space. A
classifier f : X $\rightarrow$ $\Delta$(Y) maps inputs to probability distributions over
classes. A hard-label dataset D\_hard = \{(x\_i, y\_i)\} pairs each
input with a single class label y\_i $\in$ Y. A soft-label dataset D\_soft =
\{(x\_i, q\_i)\} pairs each input with a distribution q\_i $\in$ $\Delta$(Y)
representing the empirical distribution of human annotations for
instance x\_i.

\textbf{3.2 Calibration Under Hard Labels}

A classifier \emph{f} is calibrated under hard labels if, for all
\emph{p} $\in$ {[}0, 1{]}: P(\emph{y} = argmax \emph{f}(\emph{x}) \textbar{}
max \emph{f}(\emph{x}) = \emph{p}) = \emph{p}. ECE approximates this by
partitioning predictions into \emph{M} bins {[}7{]}:

\emph{ECE = $\Sigma$$^M$$_m$$_=$$_1$ (\textbar B\_m\textbar{} / n) $\cdot$ \textbar acc(B\_m) -
conf(B\_m)\textbar{}} (1)

Temperature scaling finds T* minimizing negative log-likelihood on
D\_val, where p\_T(y \textbar{} x) = softmax(logits(x) / T) {[}7{]}:

\emph{T* = arg min\_T - (1/\textbar D\_val\textbar) $\Sigma$\_\{(x,y)$\in$D\_val\}
log p\_T(y \textbar{} x)} (2)

\textbf{3.3 Calibration Under Soft Labels}

A classifier is soft-calibrated if $^O${[}\emph{f}(\emph{x}) \textbar{}
\emph{q}(\emph{x}) = \emph{q}{]} = \emph{q} for all \emph{q} $\in$
$\Delta$(\emph{Y}). The Brier Score {[}14{]} is a strictly proper scoring rule
over soft targets:

\emph{BS = (1/n) $\Sigma$$^n$\_\{i=1\} $\Sigma$$^K$\_\{k=1\} (f\_k(x\_i) - q\_\{ik\})$^2$} (3)

\textbf{3.4 The Soft-Label Calibration Gap}

\begin{quote}
\emph{\textbf{Definition (Soft-Label Calibration Gap).} For a model f
with hard-label optimal temperature T, the soft-label calibration gap is
Gap(f, T) = BS\_soft(f\_\{T\}) - BS\_soft(f*\_\{T\_oracle\}), where
T\_oracle is the optimal temperature fitted directly against soft labels
by minimizing Equation 3. A positive gap indicates that temperature
scaling calibrated on hard labels fails to achieve the calibration
quality attainable when fitted against the true distributional target.}
\end{quote}

\textbf{4. Experimental Design}

\textbf{4.1 Datasets}

We use two publicly available soft-label datasets. CIFAR-10H {[}13{]}
provides a mean of 51 human annotations per image for all 10,000
CIFAR-10 test images. ChaosNLI {[}10{]} provides 100 human judgments per
instance for 4,645 NLI examples from SNLI (ChaosNLI-S) and MNLI
(ChaosNLI-M).

\textbf{4.2 Models}

For vision: ResNet-18 (11M), ResNet-50 (25M), ResNet-101 (44M) {[}16{]},
trained on CIFAR-10 with standard augmentation and cosine-annealed
learning rate over 100 epochs. For language: DistilBERT-base-uncased
(66M), BERT-base-uncased (110M), BERT-large-uncased (340M) {[}17{]},
fine-tuned on SNLI/MNLI for 3 epochs with lr = 2$\times$10$^{-}$$^5$ and AdamW.

\textbf{4.3 Calibration Protocol}

For each model: (1) train on hard-label training set; (2) fit T\_hard on
held-out validation split (20\%) by minimizing Eq. 2 with L-BFGS; (3)
fit T\_oracle on first half of soft-label test set by minimizing Eq. 3;
(4) evaluate both models on second half of test set; (5) compute ECE (15
bins) and Brier Score against hard and soft targets. Each configuration
repeated with seeds 42, 123, 456; we report mean and standard deviation.

\textbf{5. Results}

\textbf{5.1 Vision: CIFAR-10H}

\textbf{Table 1. Calibration results on CIFAR-10H across three ResNet
scales. Values are mean (std) over 3 seeds.}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1311}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1202}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1202}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1311}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1311}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1311}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1311}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1038}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Model}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Acc.}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Uncal ECE}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Hard ECE}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Soft ECE}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Hard BS}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Soft BS}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Gap}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
ResNet-18 & 0.898 (0.039) & 0.030 (0.006) & 0.016 (0.004) & 0.021
(0.002) & 0.127 (0.048) & 0.126 (0.049) & 0.002 (0.001) \\
ResNet-50 & 0.886 (0.003) & 0.036 (0.003) & 0.020 (0.002) & 0.022
(0.004) & 0.139 (0.003) & 0.136 (0.004) & 0.003 (0.001) \\
ResNet-101 & 0.908 (0.008) & 0.043 (0.001) & 0.018 (0.000) & 0.022
(0.006) & 0.111 (0.011) & 0.108 (0.011) & 0.003 (0.000) \\
\end{longtable}

\emph{Note. ECE = Expected Calibration Error (15 bins, vs hard argmax).
BS = Brier Score vs full soft distribution. Gap = TS-Hard BS - TS-Soft
BS. TS-Soft is an oracle condition not deployable without soft-label
calibration data.}

The soft-label calibration gap is positive for all three models (H1
supported) and increases monotonically with scale --- 0.002, 0.003,
0.003 for ResNet-18, -50, -101 (H2 supported in vision). The
T\_oracle/T\_hard ratio ranges from 1.19 to 1.32, consistent with the
low annotator disagreement rate in CIFAR-10H.

\textbf{5.2 Language: ChaosNLI}

\textbf{Table 2. Calibration results on ChaosNLI-S and ChaosNLI-M across
three BERT-family scales.}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1445}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0671}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1272}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1387}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1387}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1387}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1387}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1064}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Model}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Split}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Acc.}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Hard ECE}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Soft ECE}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Hard BS}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{TS-Soft BS}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Gap}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
DistilBERT & S & 0.748 (0.010) & 0.091 (0.010) & 0.130 (0.008) & 0.184
(0.005) & 0.140 (0.004) & 0.045 (0.001) \\
BERT-base & S & 0.712 (0.012) & 0.108 (0.010) & 0.099 (0.003) & 0.206
(0.012) & 0.156 (0.010) & 0.050 (0.002) \\
BERT-large & S & 0.570 (0.010) & 0.136 (0.011) & 0.051 (0.005) & 0.292
(0.012) & 0.240 (0.007) & 0.052 (0.006) \\
DistilBERT & M & 0.501 (0.014) & 0.241 (0.015) & 0.041 (0.005) & 0.302
(0.011) & 0.169 (0.004) & 0.134 (0.007) \\
BERT-base & M & 0.531 (0.008) & 0.204 (0.013) & 0.054 (0.016) & 0.284
(0.004) & 0.165 (0.002) & 0.119 (0.005) \\
BERT-large & M & 0.523 (0.009) & 0.149 (0.010) & 0.054 (0.011) & 0.232
(0.006) & 0.158 (0.002) & 0.074 (0.004) \\
\end{longtable}

\emph{Note. DS = ChaosNLI split (S = SNLI-derived, M = MNLI-derived).
BERT-large on ChaosNLI-S has T\_hard = 0.926; see Section 5.3.}

On ChaosNLI-S the gap increases monotonically with scale: 0.045, 0.050,
0.052 (H2 supported). The T\_oracle/T\_hard ratio is 2.3--3.5$\times$ in the
language domain versus 1.2--1.3$\times$ in vision. The gap of 0.052 for
BERT-large on ChaosNLI-S corresponds to roughly 18\% of the uncalibrated
Brier Score.

\textbf{5.3 The ChaosNLI-M Anomaly}

On ChaosNLI-M the scale ordering reverses: DistilBERT (0.134)
\textgreater{} BERT-base (0.119) \textgreater{} BERT-large (0.074). We
do not interpret this as a genuine reversal of H2. Three factors
confound the result: (1) BERT-large is already underconfident on SNLI
(T\_hard = 0.926), so its dispersed predictions can spuriously align
with ChaosNLI-M soft labels; (2) all models achieve only 50--53\%
accuracy on a three-class task, barely above chance; (3) training on
SNLI and evaluating on MNLI instances introduces an independent domain
shift. We treat this result as inconclusive with respect to H2 and flag
matched-domain evaluation as a prerequisite for a clean test in future
work.

\textbf{5.4 Temperature Ratios}

T\_oracle exceeds T\_hard in all nine configurations, ranging from 1.19
(ResNet-18) to 3.48 (DistilBERT, ChaosNLI-M). This ratio is a direct
measure of how much smoothing hard-label calibration leaves unrealized
and is consistently larger in the language domain.

\textbf{5.5 Summary of Hypothesis Outcomes}

H1 is supported across all nine configurations (SNR \textgreater{} 8 in
all cases, \textgreater{} 18 in seven of nine). H2 is supported in
vision and on ChaosNLI-S; inconclusive on ChaosNLI-M. H3 is clearly
supported: mean language gap (0.079) is approximately 30$\times$ the mean
vision gap (0.003).

\textbf{6. Implications}

\textbf{6.1 For Calibration Methodology}

These results suggest that calibration validation sets built on
majority-vote labels can systematically misstate model reliability in
ambiguous-label domains. The T\_oracle/T\_hard ratios indicate that
hard-label calibration consistently undershoots the smoothing required
to match the true soft-label target. Where feasible, practitioners
should collect repeated annotations per instance and fit calibration
parameters against the resulting distribution; our oracle results show
this requires no change to model architecture or training.

\textbf{6.2 For Large Model Deployment}

The soft-label calibration gap grows with model scale in vision and on
ChaosNLI-S, indicating that the assumption of better calibration after
standard temperature scaling can fail under soft-label evaluation and
fails more severely at higher capacity. For NLI, BERT-large achieves BS
= 0.292 under hard-label TS versus 0.240 under oracle calibration --- a
22\% relative degradation unlikely attributable to noise.

\textbf{6.3 Implications for Resource-Constrained Deployment}

The practical stakes are highest where annotation infrastructure is
weakest. In many clinical settings across sub-Saharan Africa, obtaining
many independent annotations per case is impractical. A model that
collapses clinician disagreement into an overconfident point prediction
conceals exactly the uncertainty needed for appropriate clinical
caution. We designed this study to be reproducible on freely available
compute and public data because practitioners facing this problem most
acutely often have the least access to large-scale infrastructure.

\textbf{7. Limitations}

We highlight four limitations. First, our scale range (66M--340M for
language; 11M--44M for vision) does not extend to frontier-scale models
and we make no extrapolation claim. Second, we compare temperature
scaling only against a soft-label oracle of itself; other methods such
as isotonic regression and Dirichlet calibration {[}8{]} merit
equivalent treatment. Third, the ChaosNLI-M result is confounded by
cross-domain evaluation; matched training and evaluation distributions
are needed to isolate scale effects cleanly. Fourth, both datasets
reflect annotation by English-speaking Western participants;
generalization to other linguistic and cultural contexts requires
further evidence.

\textbf{8. Conclusion}

Temperature scaling calibrated on hard labels does not fully calibrate
models when the true label distribution is soft. This gap is consistent
across all nine configurations and grows with model scale in vision and
on ChaosNLI-S. It is roughly thirty times larger in the language domain
than in vision. The reversed ordering on ChaosNLI-M is better explained
as a cross-domain confound than as a contradiction of the broader trend.

Three directions follow directly: systematic comparison of alternative
calibration methods under soft-label evaluation; extension to larger
models with matched training and evaluation distributions; and
development of a practical soft-label temperature-scaling procedure
usable with only a small number of annotations per instance.

Code: https://github.com/dogahwisdom/temperature-scaling-research

\textbf{Acknowledgments}

I am grateful to my colleagues at BlackMatrix AI Research, Accra, for
the conversations that sharpened this work and for their patience
through the long debugging sessions that preceded these results. All
experiments were conducted on freely available compute with no
institutional funding.

\textbf{References}

{[}1{]} Aroyo, L., and Welty, C. (2015). Truth is a lie: Crowd truth and
the seven myths of human annotation. \emph{AI Magazine}, 36(1), 15--24.

{[}2{]} Bai, Y., Mei, S., Wang, H., and Xiong, C. (2021).
Don\textquotesingle t just blame over-parametrization for
over-confidence: Theoretical analysis of calibration in binary
classification. \emph{Proceedings of the 38th ICML}, pp. 566--576.

{[}3{]} Wiles, O., Gowal, S., Stimberg, F., Rebuffi, S., Ktena, I.,
Dvijotham, K., and Cemgil, A. T. (2022). A fine-grained analysis on
distribution shift. \emph{Proceedings of ICLR 2022}.

{[}4{]} Guillory, D., Shankar, V., Ebrahimi, S., Darrell, T., and
Schmidt, L. (2021). Predicting with confidence on unseen distributions.
\emph{Proceedings of ICCV 2021}, pp. 1134--1144.

{[}5{]} Dawid, A. P. (1982). The well-calibrated Bayesian. \emph{Journal
of the American Statistical Association}, 77(379), 605--610.

{[}6{]} Kumar, A., Liang, P., and Ma, T. (2019). Verified uncertainty
calibration. \emph{Advances in NeurIPS}, 32.

{[}7{]} Guo, C., Pleiss, G., Sun, Y., and Weinberger, K. Q. (2017). On
calibration of modern neural networks. \emph{Proceedings of the 34th
ICML}, pp. 1321--1330.

{[}8{]} Kull, M., Perello-Nieto, M., Kangsepp, M., de Menezes e Silva
Filho, T., Song, H., and Flach, P. (2019). Beyond temperature scaling:
Obtaining well-calibrated multi-class probabilities with Dirichlet
calibration. \emph{Advances in NeurIPS}, 32.

{[}9{]} Minderer, M., Djolonga, J., Romijnders, R., Hubis, F., Zhai, X.,
Houlsby, N., Tran, D., and Lucic, M. (2021). Revisiting the calibration
of modern neural networks. \emph{Advances in NeurIPS}, 34.

{[}10{]} Nie, Y., Zhou, X., and Bansal, M. (2020). What can we learn
from collective human opinions on natural language inference data?
\emph{Proceedings of EMNLP 2020}, pp. 9131--9143.

{[}11{]} Platt, J. C. (1999). Probabilistic outputs for support vector
machines and comparisons to regularized likelihood methods. In
\emph{Advances in Large Margin Classifiers}. MIT Press, pp. 61--74.

{[}12{]} Ovadia, Y., Fertig, E., Ren, J., Nado, Z., Sculley, D.,
Nowozin, S., Dillon, J., Lakshminarayanan, B., and Snoek, J. (2019). Can
you trust your model\textquotesingle s uncertainty? Evaluating
predictive uncertainty under dataset shift. \emph{Advances in NeurIPS},
32.

{[}13{]} Peterson, J. C., Battleday, R. M., Griffiths, T. L., and
Russakovsky, O. (2019). Human uncertainty makes classification more
robust. \emph{Proceedings of ICCV 2019}, pp. 9617--9626.

{[}14{]} Brier, G. W. (1950). Verification of forecasts expressed in
terms of probability. \emph{Monthly Weather Review}, 78(1), 1--3.

{[}15{]} Raykar, V. C., Yu, S., Zhao, L. H., Valadez, G. H., Florin, C.,
Bogoni, L., and Moy, L. (2010). Learning from crowds. \emph{Journal of
Machine Learning Research}, 11, 1297--1322.

{[}16{]} He, K., Zhang, X., Ren, S., and Sun, J. (2016). Deep residual
learning for image recognition. \emph{Proceedings of CVPR 2016}, pp.
770--778.

{[}17{]} Devlin, J., Chang, M.-W., Lee, K., and Toutanova, K. (2019).
BERT: Pre-training of deep bidirectional transformers for language
understanding. \emph{Proceedings of NAACL-HLT 2019}, pp. 4171--4186.

\end{document}
